Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-11-28 Docs/IJES/journal.tex
adjusting pseudocodes

\begin{equation}
\label{linear-programming-problem}
  minf^t x \: such \; that  = 
  \begin{cases}
    A.x \leq b, \\ 
    Aeq.x = beq, \\ 
    x \geq 0.
  \end{cases}
\end{equation}

\vspace{3 mm}
In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}. The only drawback is that the found solution may not be the global minimum or maximum. Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found. The following sections describe the main features of ESBMC and $\nu$Z tools.

@@

\vspace{2 mm}
\begin{lstlisting}[label={lst:example}, language=C,numbers=left, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=b, caption={OpenMP basic Example.}]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\small,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{lstlisting}

@@

\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}

@@

\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j).
\end{align}

\vspace{2 mm}
Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints. Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as 
%
\vspace{1 mm}
\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|Ex| \leq S_0, 
\end{align}

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare hardware cost of each node as array (h)
Declare software cost of each node as array (s)
Declare communication cost of each edge (c)
Declare the initial software cost of ($S_0$)
Declare transposed incidence matrix graph G(E)
Define the solutions variable ($X_i$) as Boolean
main {
 For TipH = 0 to Hmax Do {
  Populate $X_i$ with nondeterministic / test values
  Calculate s(1-x)+c|Ex| and store at variable
  Requirement isued by Assume (Variable <= $S_0$)
  Calculate Hp cost Based on value tested of $X_i$
  Violation check with Assert(Hp > TipH)
 }
}
\end{lstlisting}

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
    if(chunk.right - chunk.left > largestChunk){
      largestChunk = chunk.right - chunk.left;
      largest = chunk;
    }
  }	
  chunks.remove(largest);	
  int median = largest.left + floor((largest.right - largest.left) / 2);
  if(median > 0){
    if(largest.right - largest.left > 1)
      chunks.add(new chunk(largest.left, median - 1));	
    if(largest.right != largest.left)
      chunks.add(new chunk(median + 1, largest.right);
  }
  return median;
}
\end{lstlisting}

@@

\vspace {2 mm}
\begin{lstlisting}[caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
step = controller.GetNextStep();
int pid = ExecuteStep(step);
while(isRunning(pid)){
  if(!controller.isNeeded(step))
    kill(pid);
}
\end{lstlisting}

@@

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
--Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and $S_0$
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G(E)
--Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
--Assert Constraints
  Add constraints (SF + CMC <= $S_0$)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{lstlisting}

>>>>

\vspace{2 mm}
\begin{equation}
\label{linear-programming-problem}
  minf^t x \: such \; that  = 
  \begin{cases}
    A.x \leq b, \\ 
    Aeq.x = beq, \\ 
    x \geq 0.
  \end{cases}
\end{equation}

\vspace{2 mm}
In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}. The only drawback is that the found solution may not be the global minimum or maximum. Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found. The following sections describe the main features of ESBMC and $\nu$Z tools.

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,label={lst:example}, language=C,numbers=left, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=b, caption={OpenMP basic Example.}]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

@@

\vspace{2.5 mm}
\begin{lstlisting}[basicstyle=\footnotesize,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{lstlisting}

@@

\vspace{-2 mm}
\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}

@@

\vspace{-3 mm}
\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j).
\end{align}

\vspace{2 mm}
Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints. Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as

\vspace{-2 mm}
\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|Ex| \leq S_0, 
\end{align}

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare hardware cost of each node as array (h)
Declare software cost of each node as array (s)
Declare communication cost of each edge (c)
Declare the initial sw cost of ($S_0$)
Declare transposed incidence matrix graph G(E)
Define the solutions ($X_i$) as Boolean
main {
 For TipH = 0 to Hmax Do {
  Populate $X_i$ with nondet / test values
  Calculate s(1-x)+c|Ex| and store at variable
  Requirement isued by Assume (variable <= $S_0$)
  Calculate Hp cost Based on value of $X_i$
  Violation check with Assert(Hp > TipH)
 }
}
\end{lstlisting}

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
 int largestChunk = -1;
 chunk largest;
 for each(chunk in chunks){
  if(chunk.right - chunk.left > largestChunk){
    largestChunk = chunk.right - chunk.left;
    largest = chunk;
  }
 }	
 chunks.remove(largest);	
 int median = largest.left + 
   floor((largest.right - largest.left) / 2);
 if(median > 0){
  if(largest.right - largest.left > 1)
   chunks.add(
     new chunk(largest.left, median - 1)
   );	
  if(largest.right != largest.left)
   chunks.add(
    new chunk(median + 1, largest.right)
   );
 }
 return median;
}
\end{lstlisting}

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
step = controller.GetNextStep();
int pid = ExecuteStep(step);
while(isRunning(pid)){
 if(!controller.isNeeded(step))
   kill(pid);
}
\end{lstlisting}

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
-Initialize Variables
 Create vZ context 
 Create binary vector (x)
 Declare number of nodes, edges and $S_0$
 Declare hardware cost of each node as array (h) 
 Declare software cost of each node as array (s)
 Declare communication cost of each edge (c)
 Declare transposed incidence matrix graph G(E)
-Arithmetic Expressions
 SC = s(1-x)
 CMC = c*|EX|
 Fobj =  x[i] * h[i]
-Assert Constraints
 Add constraints (SF + CMC <= $S_0$)
 Add constraints to minimize Fobj
 Check Model
 Print Result
\end{lstlisting}

@@
